Probability

### 2016-04-11 prob.tex
prob.lyx "1.3 Measures \mathbb{P}" Updated...

\begin{example}[Classical probability measure]
There are $2^8$ events associated with $\Omega_C$. A possible probability measure for
these events is:
\[\begin{array}{c}
\mathbb{P}(E) = \left\{ \begin{array}{ll} 
  1 & \mbox{if}~E = \Omega \\
  0 & \mbox{otherwise} 
  \end{array}\right.
\end{array}\]
\yutsung{ Actually, the above $\mathbb{P}$ is not a probability
measure because 
\[
\mathbb{P}\left(\Omega\right)=1\ne0+0=\mathbb{P}\left(E_{0}\right)+\mathbb{P}\left(E_{>0}\right)
\]
} \\
A more interesting measure is defined recursively as follows:
\renewcommand\arraystretch{1.4}
\[\begin{array}{rcl}
\mathbb{P}(\emptyset) &=& 0 \\
\mathbb{P}(\{ HHH \} \cup E) &=& \frac{1}{5} + \mathbb{P}(E) \\
\mathbb{P}(\{ HHT \} \cup E) &=& \mathbb{P}(E) \\
\mathbb{P}(\{ HTH \} \cup E) &=& \frac{3}{10} + \mathbb{P}(E) \\
\mathbb{P}(\{ HTT \} \cup E) &=& \mathbb{P}(E) \\
\mathbb{P}(\{ THH \} \cup E) &=& \frac{1}{5} + \mathbb{P}(E) \\
\mathbb{P}(\{ THT \} \cup E) &=& \mathbb{P}(E) \\
\mathbb{P}(\{ TTH \} \cup E) &=& \frac{3}{10} + \mathbb{P}(E) \\
\mathbb{P}(\{ TTT \} \cup E) &=& \mathbb{P}(E) 
\end{array}\]
\yutsung{Because $\mathbb{P}(\bigcup_{i}A_{i})=\Sigma_{i}~\mathbb{P}(A_{i})$
requires disjoint events, the above formula should write like:
\[
\begin{array}{rcl}
\mathbb{P}(\emptyset) & = & 0\\
\mathbb{P}(\{HHH\}\cup E) & = & \frac{1}{5}+\mathbb{P}(E)\textrm{, if }HHH\notin E\\
\mathbb{P}(\{HHT\}\cup E) & = & \mathbb{P}(E)\textrm{, if }HHT\notin E\\
\mathbb{P}(\{HTH\}\cup E) & = & \frac{3}{10}+\mathbb{P}(E)\textrm{, if }HTH\notin E\\
\mathbb{P}(\{HTT\}\cup E) & = & \mathbb{P}(E)\textrm{, if }HTT\notin E\\
\mathbb{P}(\{THH\}\cup E) & = & \frac{1}{5}+\mathbb{P}(E)\textrm{, if }THH\notin E\\
\mathbb{P}(\{THT\}\cup E) & = & \mathbb{P}(E)\textrm{, if }THT\notin E\\
\mathbb{P}(\{TTH\}\cup E) & = & \frac{3}{10}+\mathbb{P}(E)\textrm{, if }TTH\notin E\\
\mathbb{P}(\{TTT\}\cup E) & = & \mathbb{P}(E)\textrm{, if }TTT\notin E
\end{array}
\]
Or add a sentence ``where the element in the singleton set is not
belong to $E$ for each equation.'' We may also write like this:
\[
\begin{array}{rcl}
\mathbb{P}(\{HHH\}) & = & \frac{1}{5}\\
\mathbb{P}(\{HHT\}) & = & 0\\
\mathbb{P}(\{HTH\}) & = & \frac{3}{10}\\
\mathbb{P}(\{HTT\}) & = & 0\\
\mathbb{P}(\{THH\}) & = & \frac{1}{5}\\
\mathbb{P}(\{THT\}) & = & 0\\
\mathbb{P}(\{TTH\}) & = & \frac{3}{10}\\
\mathbb{P}(\{TTT\}) & = & 0\\
\mathbb{P}(E) & = & \sum_{\omega\in E}\mathbb{P}(\left\{ \omega\right\} )
\end{array}
\]
} \\
Because this is a \emph{classical} situation, the probability
assignments can be understood \emph{locally} and
\emph{non-contextually}. In other words, we can reason about each coin
separately and perform experiments on it ignoring the rest of the
context. If we were to perform such experiments we may find that for
the first coin, the probability of either outcome
$H$ or $T$ is $\frac{1}{2}$; for coin two, the probabilities are
skewed a little with the probability of outcome $H$ being
$\frac{2}{5}$ and the probability of outcome $T$ being $\frac{3}{5}$; and that
coin 3 is a fake double-headed coin where the probability of
outcome $H$ is 1 and the probability of outcome $T$ is 0. The reader
may check that these local observations are consistent with the
probability measure above. 
\end{example}

\begin{example}{[}Quantum probability measure{]} Like in the classical
case, there are $2^{8}$ events. But as Mermin explains in a simple
example~\cite{MerminPRL1990}, here is a possible probability measure:
\[
\begin{array}{rcl}
\mathbb{P}_{xxx}(\{LLL\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{LLR\}) & = & 0\\
\mathbb{P}_{xxx}(\{LRL\}) & = & 0\\
\mathbb{P}_{xxx}(\{LRR\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RLL\}) & = & 0\\
\mathbb{P}_{xxx}(\{RLR\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RRL\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RRR\}) & = & 0\\
\mathbb{P}_{xxx}(E) & = & \sum_{\omega\in E}\mathbb{P}_{xxx}(\left\{ \omega\right\} )
\end{array}
\]
In contrast with the classical example previously, the event of different
electrons are not independent or correlated. More precisely, consider
the event for each electron separately:
\begin{eqnarray*}
F_{1,L} & = & \left\{ LLL,LLR,LRL,LRR\right\} \\
F_{2,L} & = & \left\{ LLL,LLR,RLL,RLR\right\} \\
F_{3,L} & = & \left\{ LLL,LRL,RLL,RRL\right\} 
\end{eqnarray*}
They are correlated means 
\[
\mathbb{P}_{xxx}(F_{1,L}\cap F_{2,L}\cap F_{3,L})=\mathbb{P}_{xxx}(\{LLL\})=\frac{1}{4}\ne\frac{1}{8}=\mathbb{P}_{xxx}(F_{1,L})\mathbb{P}_{xxx}(F_{2,L})\mathbb{P}_{xxx}(F_{3,L})\textrm{ .}
\]

Classical events may also be correlated even they come from different
sources. A typical example is events defined by the temperature is
highly likely correlated to the event related to how Coca Cola is
sold. Another example are the same events we discussed in coin-tossing.
However, this time the coins are tossed behind a veil, and somebody
tosses the three coins for you. Because she tosses the coins behind
a veil, she might actually roll an tetrahedron die with $\{HHH,HTT,THT,TTH\}$
in its four faces. If $HTT$ were face-down, she places three coins
with $H$, $T$, and $T$ face-up, respectively. Then, she uncovers
the veil, and claims she has tossed the coins. Then, the result of
coin-tossing is correlated, and we will never see $TTT$ if the coins
are tossed in this way.

Because we do not know how nature decides the spin of an electron,
Einstein, Podolsky, and Rosen (EPR)~\cite{EPR1935} suggested the
nature might give us the probability measure~$\mathbb{P}_{xxx}$
because she rolled an tetrahedron die or performed other classical
and deterministic process behind the veil. This claim is convincing
if $\mathbb{P}_{xxx}$ is the only probability measure we have, but
will lead to a contradiction if we consider other probability measures
all together. Notice that after the coins are placed before uncovering
the veil, which face of a coin is up is decided although we do not
know. This would be also true for the quantum probability measure.
Because the three electrons can be specially separated, and each electron
can be measured along the $x$ axis separately, if the nature rolled
the tetrahedron die, this die should be rolled before the electrons
are separated and measured, and she should know the result of measurement.
Let the result of the $j$-th electron measured along the $x$ axis
be $w\left(\sigma_{x}^{j}\right)$ so that $w\left(\sigma_{x}^{1}\right)w\left(\sigma_{x}^{2}\right)w\left(\sigma_{x}^{3}\right)\in\{LLL,LRR,RLR,RRL\}$,
i.e., the number of $L$ in $w\left(\sigma_{x}^{1}\right)$, $w\left(\sigma_{x}^{2}\right)$,
and $w\left(\sigma_{x}^{3}\right)$ should be odd.

The interesting part is that three electrons cannot be measured the
spin only along the $x$ axis, but also along the $y$ axis with the
result down ($D$) or up ($U$). We only consider to measure even
number of electrons along the $y$ axis, and the probability measure
of non-singleton set should be computed by $\mathbb{P}_{ijk}(E)=\sum_{\omega\in E}\mathbb{P}_{ijk}(\left\{ \omega\right\} )$.
\begin{eqnarray*}
\begin{array}{rcl}
\mathbb{P}_{xyy}(\{LDD\}) & = & 0\\
\mathbb{P}_{xyy}(\{LDU\}) & = & \frac{1}{4}\\
\mathbb{P}_{xyy}(\{LUD\}) & = & \frac{1}{4}\\
\mathbb{P}_{xyy}(\{LUU\}) & = & 0\\
\mathbb{P}_{xyy}(\{RDD\}) & = & \frac{1}{4}\\
\mathbb{P}_{xyy}(\{RDU\}) & = & 0\\
\mathbb{P}_{xyy}(\{RUD\}) & = & 0\\
\mathbb{P}_{xyy}(\{RUU\}) & = & \frac{1}{4}
\end{array} & \begin{array}{rcl}
\mathbb{P}_{yxy}(\{DLD\}) & = & 0\\
\mathbb{P}_{yxy}(\{DLU\}) & = & \frac{1}{4}\\
\mathbb{P}_{yxy}(\{DRD\}) & = & \frac{1}{4}\\
\mathbb{P}_{yxy}(\{DRU\}) & = & 0\\
\mathbb{P}_{yxy}(\{ULD\}) & = & \frac{1}{4}\\
\mathbb{P}_{yxy}(\{ULU\}) & = & 0\\
\mathbb{P}_{yxy}(\{URD\}) & = & 0\\
\mathbb{P}_{yxy}(\{URU\}) & = & \frac{1}{4}
\end{array} & \begin{array}{rcl}
\mathbb{P}_{yyx}(\{DDL\}) & = & 0\\
\mathbb{P}_{yyx}(\{DDR\}) & = & \frac{1}{4}\\
\mathbb{P}_{yyx}(\{DUL\}) & = & \frac{1}{4}\\
\mathbb{P}_{yyx}(\{DUR\}) & = & 0\\
\mathbb{P}_{yyx}(\{UDL\}) & = & \frac{1}{4}\\
\mathbb{P}_{yyx}(\{UDR\}) & = & 0\\
\mathbb{P}_{yyx}(\{UUL\}) & = & 0\\
\mathbb{P}_{yyx}(\{UUR\}) & = & \frac{1}{4}
\end{array}
\end{eqnarray*}
Similarly, the nature should predetermine $w\left(\sigma_{x}^{j}\right)$
and $w\left(\sigma_{y}^{j}\right)$ for these probabilities. Furthermore,
because she do not know along which axis we are going to measure,
she should predetermine the same $w\left(\sigma_{x}^{j}\right)$ and
$w\left(\sigma_{y}^{j}\right)$ for all different probabilities. Notice
that the number of $L$ or $D$ in $\left\{ w\left(\sigma_{x}^{1}\right),w\left(\sigma_{y}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,
$\left\{ w\left(\sigma_{y}^{1}\right),w\left(\sigma_{x}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,
and $\left\{ w\left(\sigma_{y}^{1}\right),w\left(\sigma_{y}^{2}\right),w\left(\sigma_{x}^{3}\right)\right\} $
should be even. If we look these 9 letters carefully, we can find
every $w\left(\sigma_{x}^{j}\right)$ appear once and every $w\left(\sigma_{y}^{j}\right)$
appear twice. Hence, the number of $L$ in $w\left(\sigma_{x}^{1}\right)$,
$w\left(\sigma_{x}^{2}\right)$, and $w\left(\sigma_{x}^{3}\right)$
should be even. This contradict to the conclusion in our last paragraph.
Therefore, EPR's assumption is wrong, and it is not always true that
the nature can predetermine the measurement result before we perform
the measurement. \end{example}

>>>>

\begin{example}[Classical probability measure]
There are $2^8$ events associated with $\Omega_C$. A possible probability measure for
these events is:
\[\begin{array}{c}
\mathbb{P}(E) = \left\{ \begin{array}{ll} 
  1 & \mbox{if}~E = \Omega \\
  0 & \mbox{otherwise} 
  \end{array}\right.
\end{array}\]
\yutsung{ Actually, the above $\mathbb{P}$ is not a probability
measure because 
\[
\mathbb{P}\left(\Omega\right)=1\ne0+0=\mathbb{P}\left(E_{0}\right)+\mathbb{P}\left(E_{>0}\right)
\]
} \\
A more interesting measure is defined recursively as follows:
\renewcommand\arraystretch{1.4}
\[\begin{array}{rcl}
\mathbb{P}(\emptyset) &=& 0 \\
\mathbb{P}(\{ HHH \} \cup E) &=& \frac{1}{5} + \mathbb{P}(E) \\
\mathbb{P}(\{ HHT \} \cup E) &=& \mathbb{P}(E) \\
\mathbb{P}(\{ HTH \} \cup E) &=& \frac{3}{10} + \mathbb{P}(E) \\
\mathbb{P}(\{ HTT \} \cup E) &=& \mathbb{P}(E) \\
\mathbb{P}(\{ THH \} \cup E) &=& \frac{1}{5} + \mathbb{P}(E) \\
\mathbb{P}(\{ THT \} \cup E) &=& \mathbb{P}(E) \\
\mathbb{P}(\{ TTH \} \cup E) &=& \frac{3}{10} + \mathbb{P}(E) \\
\mathbb{P}(\{ TTT \} \cup E) &=& \mathbb{P}(E) 
\end{array}\]
\yutsung{Because $\mathbb{P}(\bigcup_{i}A_{i})=\Sigma_{i}~\mathbb{P}(A_{i})$
requires disjoint events, the above formula should write like:
\[
\begin{array}{rcl}
\mathbb{P}(\emptyset) & = & 0\\
\mathbb{P}(\{HHH\}\cup E) & = & \frac{1}{5}+\mathbb{P}(E)\textrm{, if }HHH\notin E\\
\mathbb{P}(\{HHT\}\cup E) & = & \mathbb{P}(E)\textrm{, if }HHT\notin E\\
\mathbb{P}(\{HTH\}\cup E) & = & \frac{3}{10}+\mathbb{P}(E)\textrm{, if }HTH\notin E\\
\mathbb{P}(\{HTT\}\cup E) & = & \mathbb{P}(E)\textrm{, if }HTT\notin E\\
\mathbb{P}(\{THH\}\cup E) & = & \frac{1}{5}+\mathbb{P}(E)\textrm{, if }THH\notin E\\
\mathbb{P}(\{THT\}\cup E) & = & \mathbb{P}(E)\textrm{, if }THT\notin E\\
\mathbb{P}(\{TTH\}\cup E) & = & \frac{3}{10}+\mathbb{P}(E)\textrm{, if }TTH\notin E\\
\mathbb{P}(\{TTT\}\cup E) & = & \mathbb{P}(E)\textrm{, if }TTT\notin E
\end{array}
\]
Or add a sentence ``where the element in the singleton set is not
belong to $E$ for each equation.'' Or write like: 
\[
\begin{array}{rcl}
\mathbb{P}(\{HHH\}) & = & \frac{1}{5}\\
\mathbb{P}(\{HHT\}) & = & 0\\
\mathbb{P}(\{HTH\}) & = & \frac{3}{10}\\
\mathbb{P}(\{HTT\}) & = & 0\\
\mathbb{P}(\{THH\}) & = & \frac{1}{5}\\
\mathbb{P}(\{THT\}) & = & 0\\
\mathbb{P}(\{TTH\}) & = & \frac{3}{10}\\
\mathbb{P}(\{TTT\}) & = & 0\\
\mathbb{P}(E) & = & \sum_{\omega\in E}\mathbb{P}(\left\{ \omega\right\} )
\end{array}
\]
} \\
Because this is a \emph{classical} situation, the probability
assignments can be understood \emph{locally} and
\emph{non-contextually}. In other words, we can reason about each coin
separately and perform experiments on it ignoring the rest of the
context. If we were to perform such experiments we may find that for
the first coin, the probability of either outcome
$H$ or $T$ is $\frac{1}{2}$; for coin two, the probabilities are
skewed a little with the probability of outcome $H$ being
$\frac{2}{5}$ and the probability of outcome $T$ being $\frac{3}{5}$; and that
coin 3 is a fake double-headed coin where the probability of
outcome $H$ is 1 and the probability of outcome $T$ is 0. The reader
may check that these local observations are consistent with the
probability measure above. 
\end{example}

\begin{example}{[}Quantum probability measure{]} Like in the classical
case, there are $2^{8}$ events. But as Mermin explains in a simple
example~\cite{MerminPRL1990}, here is a possible probability measure:
\[
\begin{array}{rcl}
\mathbb{P}_{xxx}(\{LLL\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{LLR\}) & = & 0\\
\mathbb{P}_{xxx}(\{LRL\}) & = & 0\\
\mathbb{P}_{xxx}(\{LRR\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RLL\}) & = & 0\\
\mathbb{P}_{xxx}(\{RLR\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RRL\}) & = & \frac{1}{4}\\
\mathbb{P}_{xxx}(\{RRR\}) & = & 0\\
\mathbb{P}_{xxx}(E) & = & \sum_{\omega\in E}\mathbb{P}_{xxx}(\left\{ \omega\right\} )
\end{array}
\]
In contrast with the classical example previously, the event of different
electrons are not independent. More precisely, consider the event
for each electron separately:
\begin{eqnarray*}
F_{1,L} & = & \left\{ LLL,LLR,LRL,LRR\right\} \\
F_{2,L} & = & \left\{ LLL,LLR,RLL,RLR\right\} \\
F_{3,L} & = & \left\{ LLL,LRL,RLL,RRL\right\} 
\end{eqnarray*}
They are not independent means 
\[
\mathbb{P}_{xxx}(F_{1,L}\cap F_{2,L}\cap F_{3,L})=\mathbb{P}_{xxx}(\{LLL\})=\frac{1}{4}\ne\frac{1}{8}=\mathbb{P}_{xxx}(F_{1,L})\mathbb{P}_{xxx}(F_{2,L})\mathbb{P}_{xxx}(F_{3,L})\textrm{ .}
\]

Classical events may also not be independent even if they seems unrelated.
For example, events defined by the temperature is usually not independent
to ones defined by how much Coca Cola is sold. Another example can
be formulated by tossing three coins as we discussed previously. However,
this time the coins are tossed behind a veil where someone tosses
the coins for you. Because we cannot see how she tosses the coins,
she might actually roll an tetrahedron die with $\{HHH,HTT,THT,TTH\}$
in its four faces. If $HTT$ is face-down, she faces $H$, $T$, and
$T$ up by hand, respectively. Then, she uncovers the veil, and claims
she has tossed the coins. If the coins are tossed in this way, the
result of coin-tossing is correlated, and we will never see $TTT$
no matter how many times we toss these coins.

Because we do not know how nature decides the spin of an electron,
Einstein, Podolsky, and Rosen (EPR)~\cite{EPR1935} suggested the
nature might give us the probability measure~$\mathbb{P}_{xxx}$
because she rolled an tetrahedron die or performed other classical
and deterministic process behind the veil. This claim may be convincing
if $\mathbb{P}_{xxx}$ is the only probability measure we have, but
will lead to a contradiction if we consider other probability measures
as well. Notice that after the coins are placed by hand and before
uncovering the veil, which side up has already been decided although
we do not know. This would be also true for the quantum probability
measure. Because the three electrons can be spacially separated, and
each electron can be measured along the $x$ axis separately, if the
nature rolled a tetrahedron die, this die should be rolled before
the electrons are separated and measured, and she should know the
result of measurement. Let the result of the $j$-th electron measured
along the $x$ axis be $w\left(\sigma_{x}^{j}\right)$. Because 
\[
\mathbb{P}_{xxx}(\{LLR\})=\mathbb{P}_{xxx}(\{LRL\})=\mathbb{P}_{xxx}(\{RLL\})=\mathbb{P}_{xxx}(\{RRR\})=0\textrm{ ,}
\]
we have $w\left(\sigma_{x}^{1}\right)w\left(\sigma_{x}^{2}\right)w\left(\sigma_{x}^{3}\right)\in\{LLL,LRR,RLR,RRL\}$,
i.e., the number of $L$ in $w\left(\sigma_{x}^{1}\right)$, $w\left(\sigma_{x}^{2}\right)$,
and $w\left(\sigma_{x}^{3}\right)$ should be odd.

The interesting part is that three electrons cannot be measured the
spin only along the $x$ axis, but also along the $y$ axis with the
result down ($D$) or up ($U$). We only consider to measure even
number of electrons along the $y$ axis, and the probability measure
of non-singleton set could be defined by 
\begin{eqnarray*}
\begin{array}{rcl}
\mathbb{P}_{xyy}(\{LDD\}) & = & 0\\
\mathbb{P}_{xyy}(\{LDU\}) & = & \frac{1}{4}\\
\mathbb{P}_{xyy}(\{LUD\}) & = & \frac{1}{4}\\
\mathbb{P}_{xyy}(\{LUU\}) & = & 0\\
\mathbb{P}_{xyy}(\{RDD\}) & = & \frac{1}{4}\\
\mathbb{P}_{xyy}(\{RDU\}) & = & 0\\
\mathbb{P}_{xyy}(\{RUD\}) & = & 0\\
\mathbb{P}_{xyy}(\{RUU\}) & = & \frac{1}{4}
\end{array} & \begin{array}{rcl}
\mathbb{P}_{yxy}(\{DLD\}) & = & 0\\
\mathbb{P}_{yxy}(\{DLU\}) & = & \frac{1}{4}\\
\mathbb{P}_{yxy}(\{DRD\}) & = & \frac{1}{4}\\
\mathbb{P}_{yxy}(\{DRU\}) & = & 0\\
\mathbb{P}_{yxy}(\{ULD\}) & = & \frac{1}{4}\\
\mathbb{P}_{yxy}(\{ULU\}) & = & 0\\
\mathbb{P}_{yxy}(\{URD\}) & = & 0\\
\mathbb{P}_{yxy}(\{URU\}) & = & \frac{1}{4}
\end{array} & \begin{array}{rcl}
\mathbb{P}_{yyx}(\{DDL\}) & = & 0\\
\mathbb{P}_{yyx}(\{DDR\}) & = & \frac{1}{4}\\
\mathbb{P}_{yyx}(\{DUL\}) & = & \frac{1}{4}\\
\mathbb{P}_{yyx}(\{DUR\}) & = & 0\\
\mathbb{P}_{yyx}(\{UDL\}) & = & \frac{1}{4}\\
\mathbb{P}_{yyx}(\{UDR\}) & = & 0\\
\mathbb{P}_{yyx}(\{UUL\}) & = & 0\\
\mathbb{P}_{yyx}(\{UUR\}) & = & \frac{1}{4}
\end{array}
\end{eqnarray*}
with $\mathbb{P}_{ijk}(E)=\sum_{\omega\in E}\mathbb{P}_{ijk}(\left\{ \omega\right\} )$.
Similarly, the nature should predetermine $w\left(\sigma_{x}^{j}\right)$
and $w\left(\sigma_{y}^{j}\right)$ for these probabilities. Furthermore,
because she do not know along which axis we are going to measure,
she should predetermine the same $w\left(\sigma_{x}^{j}\right)$ and
$w\left(\sigma_{y}^{j}\right)$ for all different probability measures.
Notice that the number of $L$ or $D$ in $\left\{ w\left(\sigma_{x}^{1}\right),w\left(\sigma_{y}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,
$\left\{ w\left(\sigma_{y}^{1}\right),w\left(\sigma_{x}^{2}\right),w\left(\sigma_{y}^{3}\right)\right\} $,
and $\left\{ w\left(\sigma_{y}^{1}\right),w\left(\sigma_{y}^{2}\right),w\left(\sigma_{x}^{3}\right)\right\} $
should be even. If we look these 9 letters carefully, we can find
every $w\left(\sigma_{x}^{j}\right)$ appear once and every $w\left(\sigma_{y}^{j}\right)$
appear twice. Hence, the number of $L$ in $w\left(\sigma_{x}^{1}\right)$,
$w\left(\sigma_{x}^{2}\right)$, and $w\left(\sigma_{x}^{3}\right)$
should be even. This contradict to the conclusion in our last paragraph.
Therefore, EPR's assumption is wrong, and it is not always true that
the nature can predetermine the measurement result before we perform
the measurement. \end{example}
